\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2023-09-26 paper/main.tex
CH: Polishing the abstract

\title{\bf  \sffamily \LARGE Evolution of reciprocity among individuals\\ with
limited payoff memory\\}
\date{}
\author{\parbox[c]{16cm}{\centering \onehalfspacing 
Nikoleta E. Glynatsi$^1$, Christian Hilbe$^1$, Alex McAvoy$^{2,3}$\\
$^{\rm 1}$Max Planck Research Group on the Dynamics of Social Behavior,\\ Max Planck Institute for Evolutionary Biology, Pl\"{o}n, Germany \\
$^{\rm 2}$School of Data Science and Society, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599 \\
$^{\rm 3}$Department of Mathematics, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599}}

@@

\begin{abstract}
\noindent
Models of direct reciprocity explain how cooperation can emerge in repeated social dilemmas. 
According to this literature, individuals should naturally learn to adopt conditionally cooperative strategies if further encounters are sufficiently likely.  
While such models have shaped our understanding of cooperation, they often make idealized assumptions on how individuals remember and process information. 
For example, when strategies are transmitted through social learning, it is commonly assumed that individuals update their strategies based on the resulting average payoff.  
This would require them to compute (or remember) their payoffs against all other population members. 
Instead, individuals may sometimes update their strategies based on their most recent experiences only. 
Herein, we introduce a theoretical framework to study the evolution of reciprocity when individuals only learn based on the outcome of their very last interaction. 
%We compare this model to the classical framework based on expected payoffs.  
We show that cooperation can still evolve, but individuals adopt less generous strategies, and they tend to cooperate less often than in the classical framework based on expected payoffs. 
Interestingly, however, we also show that once individuals remember the payoffs of two or three interactions, evolving cooperation rates approach the results of the classical model. 
These findings contribute to a literature that explores which kind of cognitive capabilities are required for reciprocal cooperation. While our results suggest that more memory facilitates the evolution of reciprocity, it only takes a modest amount of payoff memory for cooperation to emerge. 
\end{abstract}

>>>>

\title{\bf  \sffamily \Large Evolution of reciprocity %among individuals\\ 
with limited payoff memory\\}
\date{}
\author{\parbox[c]{16cm}{\centering \onehalfspacing 
Nikoleta E. Glynatsi$^1$,  Alex McAvoy$^{2,3}$, Christian Hilbe$^1$\\
$^{\rm 1}$Max Planck Research Group on the Dynamics of Social Behavior,\\ Max Planck Institute for Evolutionary Biology, Pl\"{o}n, Germany \\
$^{\rm 2}$School of Data Science and Society, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599 \\
$^{\rm 3}$Department of Mathematics, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599}}

@@

\begin{abstract}
\noindent
Models of direct reciprocity explain how cooperation can emerge in repeated social dilemmas. 
According to this literature, individuals should naturally learn to adopt conditionally cooperative strategies if they expect to have further encounters with their interaction partner. 
While models of reciprocity have shaped our understanding of cooperation, they often make idealized assumptions on how individuals remember and process information. 
For example, when strategies change through social learning, it is commonly assumed that individuals take into account the strategy's average payoff.  
However, this would require them to compute (or remember) their payoffs against all other population members.
Instead, individuals may sometimes update their strategies based on their most recent experiences only. 
Herein, we introduce a theoretical framework to study the evolution of reciprocity when individuals only learn based on the outcome of their very last interaction. 
%We compare this model to the classical framework based on expected payoffs.  
We show that cooperation can still evolve, but individuals adopt less generous strategies, and they tend to cooperate less often than in the classical framework based on expected payoffs. 
Interestingly, however, we also show that once individuals remember the payoffs of two or three interactions, evolving cooperation rates approach the results of the classical model. 
These findings contribute to a literature that explores which kind of cognitive capabilities are required for reciprocal cooperation. While our results suggest that more memory facilitates the evolution of reciprocity, it only takes a modest amount of payoff memory for cooperation to emerge. 
\end{abstract}
